Supplementary material for: \nA comparison of single-cell trajectory inference methods

### 2018-11-12 manuscript/supplementary.Rmd

---
title: "Supplementary material for: \nA comparison of single-cell trajectory inference methods: towards more accurate and robust tools"
output: 
  dynbenchmark::pdf_manuscript:
      render_change: FALSE
---

>>>>

---
title: "Supplementary material for: \nA comparison of single-cell trajectory inference methods"
output: 
  dynbenchmark::pdf_manuscript:
      render_change: FALSE
---
